---
title: "Go: Easy set up for R courses from ITS"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This Repo contains code that helps set up your computer and R session for ITS Courses or to use ITS developed R packages.

When using R you often need to have installed the correct version, have the correct packages and dependencies, and access to the correct data and API keys. This can be difficult to convey to beginners or require intimidating long lists of prerequisites. So we have condensed the whole process down into a single one-line command that is easy to use.

For example, to set up your computer for the PCT Advanced Training Course simply:

- Open R Studio
- Type or Copy the following command into the console
```{r demo, echo = TRUE, eval = FALSE}
source("https://git.io/fj9eC")
```
- Press Enter

This simple command will check your computer, install all the necessary packages and tell you if your computer is ready to be used for the course.